### 2021-03-24 latex/SM.tex
update

\subsection{Lepton mixing}
In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \label{eq:YukawaLagrangian}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
\end{align}
has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
\begin{align}\label{eq:leptonYukawaDiag}
    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
\end{align}
This procedure give the lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
\begin{align}
    \label{eq:j_CC}
    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
\end{align}
where each fermion field and matrix have an implied $L$ subscript which was dropped for clarity. The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$. However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since any flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.

The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. When we introduce neutrino mixing, this conservation will be broken. 
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}

>>>>

\subsection{Lepton mixing}
In the unitary gauge, the Higgs-lepton Yukawa Lagrangian 
\begin{align}
    \label{eq:YukawaLagrangian}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime}
\end{align}
has a non-diagonal Yukawa coupling matrix $Y^{\prime \ell}$, which results in the lepton masses being non-definite. This can be remedied by diagonalizing $Y^{\prime \ell}$ with a unitary matrix $V^\ell$
\begin{align}\label{eq:leptonYukawaDiag}
    V_{L}^{\ell \dagger} Y^{\prime \ell} V_{R}^{\ell}=Y^{\ell}\,.
\end{align}
This procedure give the lepton fields $\ell_{X}=V_{X}^{\ell \dagger} \ell_{X}^{\prime}$ definite mass. However, this alters the form of the neutral and charged current interactions, which the neutrinos undergo. The leptonic charged weak current now takes the form
\begin{align}
    \label{eq:j_CC}
    j^\rho_W &= 2 \bar{\nu}^\prime_\alpha \gamma^\rho \ell^\prime_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha V^{\ell \dagger} \gamma^\rho V^\ell \ell_\alpha \nonumber \\
             &= 2 \bar{\nu}_\alpha \gamma^\rho \ell_\alpha\,,
\end{align}
where each fermion field and matrix have an implied $L$ subscript which was dropped for clarity. The flavor neutrino fields $\nu_\alpha$ now only couple to the associated charged lepton field $\ell_\alpha$. However, since we still operate under the SM framework, $\nu_\alpha$ is still massless, since no flavor rotation $V_{L}^{\ell \dagger}$ can make massless fields massive.

The leptonic current in Eq.~\ref{eq:j_CC} implies that the lepton number $L_\alpha$ is conserved. 
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}

### 2021-03-24 latex/nsi.tex
update

\documentclass[twocolumn]{article}
\input{commands.tex}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}

\begin{document}
Just as we before only considered matter interactions with electrons, we can extend this to include the up and down quarks which are present in the Earth as components of neutrons and protons. 
Consider interactions beyond the Standard Model through the following Lagrangians,
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with $f \in \{e,u,d\}$. 
\bibliographystyle{apalike}
\bibliography{ref}
\end{document}

>>>>

\documentclass[twocolumn]{article}
\input{commands.tex}
\usepackage{physics,amsmath, amsfonts, siunitx, amssymb,cite}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\externaldocument{SM}

\begin{document}
\section{Non-Standard Interactions}
Just as we before only considered matter interactions with electrons, we can extend this to include the up and down quarks which are present in the Earth as components of neutrons and protons. 
Consider interactions beyond the Standard Model through the following Lagrangians,
\begin{align*}
    \mathcal{L}_{\mathrm{CC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f f^{\prime} X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \ell_{\beta}\right)\left(\bar{f}^{\prime} \gamma_{\mu} P_{X} f\right) \\
    \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align*}
where CC denotes the charged current interaction with the matter field $f\neq f^\prime \in \{u,d\}$, and NC denotes the neutral current interaction with $f \in \{e,u,d\}$.

We have no independent sensitivity for the neither chirality nor flavor type of $\varepsilon^X$, so we sum over these and study the effective matter NSI parameter $\varepsilon_{\ab}$:
\begin{align}
    \varepsilon_{\ab} = \sum_{X \in \{L,R\}} \sum_{f \in \{e,u,d\}} \frac{N_f}{N_e} \varepsilon^{fX}_{\ab}\,.
\end{align}
Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, we get $N_u/N_e \simeq U_d/N_e \simeq 3$. Thus,
\begin{align}
    \varepsilon_{\ab} =  \sum_X [\varepsilon_{\ab}^{eX} + 3(\varepsilon_{\ab}^{uX} + \varepsilon_{\ab}^{dX})]
\end{align}
Now, $\varepsilon_{\ab}$ enters the Hamiltonian as entries of a potential-like matrix:
\begin{align}\label{eq:NSIH}
    H &= \frac{1}{2E} \left[UMU^\dagger + A_{CC}\text{diag}(1,0,0,\kappa) + A_{CC} \varepsilon \right] \nonumber \\
      &= \frac{1}{2E} \left[UMU^\dagger + A_{CC}
      \begin{pmatrix}
          1 + \varepsilon_{ee} & \varepsilon_{e\mu} & \varepsilon_{e\tau} & \varepsilon_{es} \\
          \varepsilon_{\mu e} & \varepsilon_{\mu\mu} & \varepsilon_{\mu\tau} & \varepsilon_{\mu s} \\
          \varepsilon_{\tau e} & \varepsilon_{\tau\mu} & \varepsilon_{\tau\tau} & \varepsilon_{\tau s} \\
          \varepsilon_{ss} & \varepsilon_{s\mu} & \varepsilon_{s\tau} & \kappa+\varepsilon_{ss} \\
      \end{pmatrix} \right]\,, 
\end{align}
where $\kappa$ denotes the ratio $A_{NC}/A_{CC} = N_n/2N_e$ and can be taken to be $\simeq 0.5$ since $N_n/N_e\simeq 1$.

We can draw several conclusions from this form of the Hamiltonian. The any nonzero off-diagonal element $\varepsilon_{\ab}, \a \neq \b$ will make the NSI violate lepton flavor, just as the off-diagonal elements of $U$ does in the SM. Moreover, since both SM potential entries are of $\mathcal{O}(1)$, any $\varepsilon_{\ab} \sim 1$ will make the new matter effect be the same order as the SM effect.
As in Ref.~\cite{tommyNSI}, $\varepsilon_{\ab}$ have the scale
\begin{align}
    \varepsilon_{\ab} \propto \frac{m_W^2}{m_{\varepsilon}^2} \sim \frac{10^{-2}}{m_\varepsilon^2}\,
\end{align} 
in TeV, so the new interactions generated at a mass scale of $m_\varepsilon = \SI{1}{TeV}$ will produce NSI parameters in the order of $10^{-2}$, , two magnitudes below the SM matter effect. Thus, if we assume the new interactions to arise from a higher-energy theory at or above TeV scale, we then predict that the NSI parameters contribute at most $10^{-2}$ to the SM matter effect, decreasing quadratically. 
\bibliographystyle{apalike}
\bibliography{ref}
\end{document}

### 2021-03-24 latex/oscillations.tex
update

\begin{document}
\section{Sterile and Massive Neutrinos}\label{ch:sterile}
As we saw in Eq.~\ref{eq:j_CC}
, the neutrino fields $\nu_\alpha$ only couple to the associated lepton fields $\ell_\alpha$, conserving the lepton number $L_\alpha$. We will now introduce two separate extensions to this part of the Standard Model.

@@

\begin{align}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]
\end{align}
Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
\begin{align}
    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
\end{align}
Now, let the neutrino field with chriality $X$ be denoted $n_X$, with components Latin numerals to distinguish them from the flavour components, i.e 
\begin{align}
    \nu_{k X} =  V_{kj X}^{\nu \dagger} \nu_{jX}^\prime\,.
\end{align}
The diagonalized Lagrangian now takes the form 
\begin{align}
    \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right.\\
    &\hspace{5.7em}+\left. \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
\end{align}
Now using the fact that $Y^\nu_{kj}$ is diagonal, we write it as $Y_{k j}^{\nu}=y_{k}^{\nu} \delta_{k j}$, leaving the Lagrangian as 
\begin{align}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
\end{align}

Now, the Dirac neutrino field is
\begin{align}
    \nu_k = \nu_{kL} + \nu_{kR}\,.
\end{align}
Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
\begin{align}
    \bar{\nu}_k \nu_k 
    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
\end{align}
The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs VEV into the fields gives us
\begin{align}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
\end{align}
Thus, this extension to the SM generates neutrino masses by the Higgs mechanism, in the same fashion as with the charged leptons and the quarks:
\begin{align}
    m_k = \frac{y_k^\nu v}{\sqrt{2}}
\end{align}
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}

>>>>

\begin{document}
\section{Neutrino Masses and Oscillations}\label{ch:oscillation}
As we saw in Eq.~\ref{eq:j_CC}
, the neutrino fields $\nu_\alpha$ only couple to the associated lepton fields $\ell_\alpha$, conserving the lepton number $L_\alpha$. We will now introduce two separate extensions to this part of the Standard Model.

@@

\begin{align}
    \mathcal{L}_{H}=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right]
\end{align}
Similar to how we diagonalized the lepton Yukawa couplings $Y_{\alpha \beta}^{\prime \ell}$ in Eq.~~\ref{eq:leptonYukawaDiag}, we diagonalize $Y_{\alpha \beta}^{\prime \nu}$ as
\begin{align}
    V_{\alpha k L}^{\nu \dagger} Y^{\prime \nu}_{\alpha \beta} V_{\beta j R}^{\nu}=Y^{\nu}_{kj} \,.
\end{align}
Now we introduce a crucial difference between the properties of the charged lepton and the neutrino fields.
While the charged lepton flavor eigenstate was uniquely determined by its mass eigenstate, the neutrino flavor is a superposition of mass eigenstates. This is because neutrinos are indirectly detected via the observation of its associated charged lepton, so there is no requirement of neutrino flavor eigenstates to have a definite mass. The flavor of a neutrino is then, by definition, the flavor of the associated charged lepton. This is commonly introduced as giving the mass eigenstates Latin numerals and letters, while the flavor eigenstates stay as Greek letters.

So, let the neutrino field with chriality $X$ be denoted $\nu_X$, with components having Latin numerals to distinguish them from the flavour components, i.e 
\begin{align}\label{eq:nu_rotation}
    \nu_{k X} =  V_{k\beta X}^{\nu \dagger} \nu_{\beta X}^\prime\,.
\end{align}
The diagonalized Lagrangian now takes the form 
\begin{align}
    \mathcal{L}_{H} &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \ell} \ell_{\beta R}^{\prime} + \nu_{\alpha L}^{\prime} Y_{\alpha \beta}^{\prime \nu} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^{\prime} V_{\alpha \beta L}^{\ell} Y_{\alpha \beta}^{ \ell} V_{\alpha \beta R}^{\ell \dagger} \ell_{\beta R}^{\prime}\right. \nonumber \\
    &\hspace{5.7em}+\left. \nu_{\alpha L}^{\prime} V_{\alpha k L}^{\nu} Y_{kj}^{\nu} V_{\beta j  R}^{\nu \dagger} \nu_{\beta R}^{\prime}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\ell_{\alpha L}^\dagger Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \nu_{k L}^{\dagger} Y_{kj}^{ \nu} \nu_{j R}\right] \nonumber \\
    &= -\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} Y_{\alpha \beta}^{ \ell} \ell_{\beta R} + \bar{\nu}_{k L} Y_{kj}^\nu \nu_{j R}\right]
\end{align}
By construction, $Y^\ell_{\alpha \beta}$ and $Y^\nu_{kj}$ are diagonal, so we write them as $y_{\alpha}^{\ell} \delta_{\alpha \beta}$ and $y_{k}^{\nu} \delta_{k j}$ respectively, leaving the Lagrangian as 
\begin{align}\label{eq:L_H}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell} \delta_{\alpha \beta} \ell_{\beta R} + \bar{\nu}_{k L} y_{k}^{\nu} \delta_{k j} \nu_{j R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[\bar{\ell}_{\alpha L} y_{\alpha}^{\ell}  \ell_{\alpha R} + \bar{\nu}_{k L} y_{k}^{\nu} \nu_{k R}\right] \nonumber \\
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}  \bar{\ell}_{\alpha L}\ell_{\alpha R} +  y_{k}^{\nu}\bar{\nu}_{k L} \nu_{k R}\right] 
\end{align}

Now, the Dirac neutrino field is
\begin{align}
    \nu_k = \nu_{kL} + \nu_{kR}\,.
\end{align}
Multiplying $\nu_k$ with its conjugate $\bar{\nu}_k$, we get 
\begin{align}
    \bar{\nu}_k \nu_k 
    & = \bar{\nu}_{k L} \nu_{k L} +\bar{\nu}_{k R}\nu_{k L} + \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k R} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \bar{\nu}_{k R}\nu_{k L} \nonumber \\
    & = \bar{\nu}_{k L}\nu_{k R} + \t{h.c.}
\end{align}
The same calculation for the charged lepton field yields the same result for $\ell_k$. Substituting this result and expanding the Higgs VEV into the fields gives us
\begin{align}
    \mathcal{L}_{H} 
    &=-\left( \frac{v + H}{\sqrt{2}} \right) \left[ y_{\alpha}^{\ell}   \bar{\ell}_\alpha \ell_\alpha  +  y_{k}^{\nu} \bar{\nu}_k \nu_k \right] \nonumber \\
    &=- \frac{y_{\alpha}^{\ell} v}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha   -  \frac{ y_{k}^{\nu} v}{\sqrt{2}} \bar{\nu}_k \nu_k  - \frac{y_{\alpha}^{\ell}}{\sqrt{2}}   \bar{\ell}_\alpha \ell_\alpha H  -  \frac{ y_{k}^{\nu}}{\sqrt{2}} \bar{\nu}_k \nu_k H\,.
\end{align}
Thus, this extension to the SM generates neutrino masses by the Higgs mechanism, in the same fashion as with the charged leptons and the quarks:
\begin{align}
    m_k = \frac{y_k^\nu v}{\sqrt{2}}
\end{align}

Substituting the new transformation from Eq.~\ref{eq:nu_rotation} into the weak charged current, we get
\begin{align}\label{eq:j_CC2}
    j^\rho_L &= 2\bar{\nu}^\prime_{\alpha L} \gamma^\rho \ell_{\alpha L}^\prime \nonumber \\
             &= 2\bar{\nu}_{k L} V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} \gamma^\rho  \ell_{\alpha L}
\end{align}
Call $V^{\prime \nu \dagger}_{k \alpha}V^{\prime \ell}_{\alpha \alpha} = U^\dagger_{k \alpha}$
Now, the current in Eq.~\ref{eq:j_CC2} conserves lepton number, since the neutrino field with flavor $\alpha$ only couples to the lepton field with flavor $\alpha$. However, the Higgs-lepton Yukawa Lagrangian 
in Eq.~\ref{eq:L_H} violates lepton number conservation since it couples the charged lepton flavor $\alpha$ to the neutrino mass eigenstate $k$, which is a superposition of flavors. There is no transformation that leaves both the interaction and kinetic Lagrangian invariant.
We now have 
\begin{align}
    j^\rho_L &= 2 U^*_{\alpha k} \bar{\nu}_{k L} \gamma^\rho  \ell_{\alpha L}
\end{align}

Derivation of neutrino oscillation formula
%\bibliographystyle{apalike}
%\bibliography{ref}
\end{document}
